### 2019-11-02 paper/paper.tex
title and abstract

% typesetting words
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\expres}{\project{\acronym{EXPRES}}}

@@

\section*{Method}

>>>>

% typesetting words
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\expres}{\project{\acronym{EXPRES}}}
\newcommand{\name}{\project{NameOfThis}}

@@

\section*{\raggedright%
\name:
A non-parametric, hierarchical model for a laser-comb-calibrated spectrograph}

\noindent
\textbf{Lily~Zhao} (Yale) (Flatiron),
\textbf{David~W~Hogg} (NYU) (MPIA) (Flatiron),
\ldots and others\ldots

\paragraph{Abstract:}
There have been many hardware improvements in polygonal-fiber-fed,
temperature-controlled, laser-frequency-comb or etalon-calibrated,
high-resolution, extreme-precision radial-velocity spectrographs.
Have the calibration methodologies improved to match?
Here are three relevant observations:
The first is that the calibration lines or spots from an etalon or
comb fill the spectral range with dense calibration points.
The second is that the spectrograph lives in a stabilized,
climate-controlled environment, in which the full optical system and
detectors will only vary within a tiny range of configurations or
settings.
The third is that---given this stability--- every calibration image
ever taken is relevant to every science exposure ever taken; there is
no reason to calibrate every exposure independently.
The calibration methodology we propose here---\name---addresses these
three problems by going non-parametric (no more polynomials) and then
reducing dimensionality with a robust principal-component method.
We demonstrate the success of this method with data from the
\expres\ spectrograph.
We find... [results and so on].

\section{Introduction}

\section{Method}
